Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-22 doc/JFLA2022/paper.tex
uniform typesetting of e.g., formulation improvements

\begin{figure}[h]
  \centering
  \fbox{
    \begin{minipage}[h]{1.0\linewidth}
 \inputsnippets{Hprime_HprimeDef}     
    \end{minipage}}
 \caption{$H'$ definition with the \equations
 plug-in~\cite{sozeau:hal-01671777}}
\label{fig:Hprime}
\end{figure}

@@

\paragraph{Proof engineering improvements.}
%
The original release of the Cantor library preceded support for type classes in \coq~\cite{MS08}. Changes over time before the move of \Hydras to \community have since then introduced type classes for some concepts in the Hydra-battles library related to ordinals. Most type classes initially used a \emph{semi bundled} approach~\cite{Mathlib}, but we have recently \emph{unbundled} classes to enable more sharing during resolution~\cite{BS2011}. For example, we use the (single-field) \texttt{Decision} type class~\cite{BS2011}, that describes deciding a proposition, in parameters to other classes rather than in fields. Due to the modest depth of our class hierarchy, we believe unbundling will not lead to scalability issues. Orthogonally to type classes, we introduced automation for definitions via the \equations~\cite{sozeau:hal-01671777} and Paramcoq~\cite{Keller2012} plug-ins.

@@

\Hydras wants to provide a connection between scientific literature (\emph{e.g.},~\cite{KP82, KS81, schutte}) and proof assistant technology. For the mathematician, it can give a concrete view of the mathematical content, not only through full proofs, but also through illuminating computations: examples, functions associated with constructive proofs, etc. For the \coq learner, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques. %It may be also used as a library, through opam packages.
It is also a medium sized library (more than 50,000 LOC), dependent on various tools and libraries of the \coq ecosystem, which may be also used to experiment with new maintenance techniques of the code and its documentation. To facilitate easy dissemination and reuse, all code and documentation is available under the permissive MIT license.

>>>>

\begin{figure}[h]
  \centering
  \fbox{
    \begin{minipage}[h]{1.0\linewidth}
 \inputsnippets{Hprime_HprimeDef}     
    \end{minipage}}
 \caption{$H'$ definition using the \equations plug-in.}
\label{fig:Hprime}
\end{figure}

@@

\paragraph{Proof engineering improvements.}
%
The original release of the Cantor library preceded support for type classes in \coq~\cite{MS08}.
%
Changes over time before the move of \Hydras to \community have since then introduced type classes for some concepts in the Hydra-battles library related to ordinals, e.g., to provide a uniform way to compare ordinals within different representation systems.
%
Most type classes initially used a \emph{semi bundled} approach~\cite{Mathlib}, but we have recently \emph{unbundled} classes to enable more sharing during resolution. For instance, we use the (single-field) \texttt{Decision} type class~\cite{BS2011}, that describes deciding a proposition, in parameters to other classes rather than in their fields. Due to the modest depth of our class hierarchy, we believe unbundling will not lead to scalability issues. Orthogonally to type classes, we introduced automation for definitions using the Paramcoq~\cite{Keller2012} and \equations~\cite{sozeau:hal-01671777} plug-ins, as illustrated in Figure~\ref{fig:Hprime}.

@@

\Hydras wants to provide a connection between scientific literature (e.g.,~\cite{KP82, KS81, schutte}) and proof assistant technology. For the mathematician, it can give a concrete view of the mathematical content, not only through full proofs, but also through illuminating computations: examples, functions associated with constructive proofs, etc. For the \coq learner, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques. %It may be also used as a library, through opam packages.
It is also a medium sized library (more than 50,000 LOC), dependent on various tools and libraries of the \coq ecosystem, which may be also used to experiment with new maintenance techniques of the code and its documentation. To facilitate easy dissemination and reuse, all code and documentation is available under the permissive MIT license.
